\documentclass[line,margin]{res}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

\begin{document}

\name{Quinn Shanahan}
\address{q.shanahan@gmail.com}
\address{(641) 233-1123}

\begin{resume}

    \section{OBJECTIVE}

    I am excited about the opportunity to take the next step in my career. while
    at Freshly, I've gained experience planning and executing technical projects on
    a large scale. I'm now looking to take on more challenging projects and deepen
    my technical knowledge.

    \section{SKILLS}
     {\sl Languages:}
    Go, Node / Javascript / Typescript, Ruby, Rust,
    Python, PHP, HTML5 and CSS3, Bash

        {\sl Frameworks:}
    React, Ruby on Rails, Sinatra, jQuery, Backbone, Ember,
    Meteor, Django, D3, Drupal, Twitter Bootstrap, Compass,
    Angular

        {\sl Infrastructure:}
    Terraform, Ansible, Google Cloud, AWS (S3, CloudFront, CloudFormation, EC2, etc),
    Puppet, Chef, Capistrano, Monit, Heroku, Vagrant, Ubuntu and Debian

    \section{EXPERIENCE}
     {\sl Principal Engineer, Platform}
    \hfill 2018- \\
    Freshly
    \begin{itemize} \itemsep -2pt
        \item
              Work with business and product teams to scope and plan technical
              roadmap for the engineering team

        \item
              Work with engineering leads and ICs to architect and implement
              technical roadmap
    \end{itemize}

    {\sl Lead Developer}
    \hfill 2013-14 \\
    StackSocial
    \begin{itemize} \itemsep -2pt
        \item
              Managed a team of developers at a growing start-up.

        \item
              Led a functional and design relaunch of the web
              application and storefront, as well as coordinating
              a launch of an iOS mobile application.
    \end{itemize}

    {\sl Lead Developer}
    \hfill 2010-17 \\
    HoneyCo
    \begin{itemize} \itemsep -2pt
        \item
              Built a consultancy from the ground up while leading
              a team of developers.

        \item
              Worked on interdisciplinary projects requiring skills in
              usability, planning, product planning, and user experience.

        \item
              Trained beginner developers to be adept full-stack developers.
    \end{itemize}

    {\sl Senior Consultant}
    \hfill 2009-10 \\
    Control Group
    \begin{itemize} \itemsep -2pt
        \item
              Worked on a team of developers to tackle technical problems across
              various industries and technologies.

        \item
              Modernized development pipeline, moved standard SCM to git from
              svn, promoted using tools such as Ruby on Rails and automated
              testing.

        \item
              Built scalable infrastructure using Amazon Web Services.

        \item
              Created automated full test coverage using tools such as Cucumber
              and Capybara.
    \end{itemize}

    \begin{samepage}
        {\sl Consultant}
        \hfill 2008-09 \\
        Independent
        \begin{itemize} \itemsep -2pt
            \item
                  Worked on web-based projects including intranet software, startups
                  and front-facing web applications.

        \end{itemize}
    \end{samepage}

    \begin{samepage}
        {\sl Developer}
        \hfill 2008 \\
        Scribestorm
        \begin{itemize} \itemsep -2pt
            \item
                  Built tools to help artists and musicians publish and distribute
                  their content online with a small agile team of developers.

        \end{itemize}
    \end{samepage}

    {\sl CTO}
    \hfill 2007-2008 \\
    ENN
    \begin{itemize} \itemsep -2pt
        \item
              Led a team of developers to relaunch the ENN front-end as well as
              consolidate and normalize ENN's archive of 10+ years of articles.

        \item
              Worked with ENN's stakeholders to increase the product offerings
              to include press releases as well as custom subject-matter
              specific content.
    \end{itemize}

    {\sl Front-end Developer}
    \hfill 2005-2006 \\
    ArtSelect
    \begin{itemize} \itemsep -2pt
        \item
              Worked on front-end projects for the ArtSelect e-commerce website.
    \end{itemize}

    {\sl Junior Developer}
    \hfill 2004-2005 \\
    Harper Brush
    \begin{itemize} \itemsep -2pt
        \item
              Created tools for managing and documenting Harper Brush's product
              database.

        \item
              Relaunched Harper Brush website.
    \end{itemize}

    \section{SELECTED \\ PROJECTS}
     {\sl Freshly Cloud Migration}
    \hfill 2021 \\
    data migration
    \begin{itemize} \itemsep -2pt
        \item
              Led a project to migrate Freshly's application and database from Heroku
              to Google Cloud. Through the use of ETL tools was able to perform the
              migration in a very small downtime window without incident.
    \end{itemize}

    {\sl Freshly Pack Stations}
    \hfill 2021 \\
    data migration
    \begin{itemize} \itemsep -2pt
        \item
              Led a project in collaboration with Operations to implement a new process
              in distribution centers to improve reliability and accuracy of shipped orders
              to customers.
    \end{itemize}

    {\sl Yves Tanguy Catalogue Raisonné}
    \hfill 2017 \\
    data migration
    \begin{itemize} \itemsep -2pt
        \item
              Worked with Artifex Press and The Matisse Foundation to migrate the
              research for an upcoming Yves Tanguy Catalogue Raisonné from a
              custom FileMaker database to a web based interface (artifexpress.com)
    \end{itemize}

    {\sl Artifex Press Cloud Migration}
    \hfill 2016 \\
    devops
    \begin{itemize} \itemsep -2pt
        \item
              Migrated artifexpress.com infrastructure from a dedicated virtual host to
              AWS based load-balanced ec2 instances.
    \end{itemize}

    {\sl MTA Kiosk}
    \hfill 2015 \\
    touchscreen, frontend development, development
    \begin{itemize} \itemsep -2pt
        \item
              Implemented display of train arrivals on underground kiosk
        \item
              Implemented display of bus arrivals on underground kiosk
        \item
              Implemented scrolling display of recent tweets by MTA twitter accounts
        \item
              Implemented dashboard of various status alerts for internal use by the MTA
    \end{itemize}

    {\sl SinglePlatform}
    \hfill 2014 \\
    UX, frontend development
    \begin{itemize} \itemsep -2pt
        \item
              Consulted Constant Contact's subsidiary SinglePlatform and provided guidance
              on UX based decisions on new UIs they were developing at the time.
    \end{itemize}

    {\sl PennDOT Kiosk}
    \hfill 2014 \\
    touchscreen, development
    \begin{itemize} \itemsep -2pt
        \item
              Worked with Control Group and Cambridge Systematics to build a kiosk to
              enable access to subsidized transit options for veterans, people with
              disabilities and other people who would not normally have access to them.
    \end{itemize}

    {\sl StackSocial Redesign}
    \hfill 2013 \\
    responsive design, development, devops
    \begin{itemize} \itemsep -2pt
        \item
              Led a team of designers and developers to redesign the stacksocial.com website
              and improve performance and stability of e-commerce functionality.
        \item
              Optimized databases and application servers in times of high traffic and overall
              growth.
    \end{itemize}

    {\sl Adaptly}
    \hfill 2012 \\
    Application development
    \begin{itemize} \itemsep -2pt
        \item
              Created new website at \url{http://www.adaptly.com/} as well as
              set up custom tracking using Google Analytics.

    \end{itemize}

    {\sl Long Island Index}
    \hfill 2012 \\
    Data migration, application development
    \begin{itemize} \itemsep -2pt
        \item
              Led a team of developers to relaunch
              \url{http://www.longislandindex.org/}.

        \item
              Required working with legacy data to build the database of
              research data and creating content authoring tools for the front-
              end.
    \end{itemize}

    \begin{samepage}
        {\sl Empirical Grammar}
        \hfill 2012-14 \\
        Data migration, application development
        \begin{itemize} \itemsep -2pt
            \item
                  Prototyped tools for interactive learning software including an
                  interactive textbook, an interactive history map and grammar
                  quizzes that provided scores and feedback.

            \item
                  Rapidly developed and iterated tools for presentations and grants.
        \end{itemize}
    \end{samepage}


    \begin{samepage}
        {\sl Yipit}
        \hfill 2012 \\
        Application development
        \begin{itemize} \itemsep -2pt
            \item
                  Relaunched front-end of \url{http://www.yipit.com/}.

            \item
                  Built dynamic tools for browsing and filtering deals.
        \end{itemize}
    \end{samepage}

    {\sl Styledon}
    \hfill 2011 \\
    Application development, Front-end Development
    \begin{itemize} \itemsep -2pt
        \item
              Rebuilt \url{http://www.styledon.com/} on Rails 3.2 from Rails
              2.3.

        \item
              Created new suite of content authoring tools including interactive
              uploading tools and bookmarklets.
    \end{itemize}

    {\sl IMG Fashion Week}
    \hfill 2010 \\
    Application development
    \begin{itemize} \itemsep -2pt
        \item
              Created sign-up system for IMG Fashion Week that allowed users to
              register, pay for, request and print event credentials; integrated
              system with on-site barcode readers created by Fashion GPS.
    \end{itemize}

    {\sl Neue Galerie}
    \hfill 2010 \\
    Application development
    \begin{itemize} \itemsep -2pt
        \item
              Created new website and e-commerce platform at
              \mbox{\url{http://www.neuegalerie.com/}} in collaboration with
              Pentagram.

    \end{itemize}

    \begin{samepage}
        {\sl Walker Group CRM}
        \hfill 2008 \\
        Application development
        \begin{itemize} \itemsep -2pt
            \item
                  Built CRM for Walker Group to deploy insurance adjusters
                  throughout the United States immediately after natural disasters
                  that allowed the client to send segmented emails to adjusters.

        \end{itemize}
    \end{samepage}

    \section{CONTACT}
    \vspace{-2.3ex}
    \begin{tabbing}
        \hspace{1.5in}\= \hspace{2.0in}\= \kill

        {\sl Phone}            \> (347) 469-1595 \\
        {\sl Email}            \> quinn@honeyco.nyc \\
        {\sl Personal Website} \> \url{http://quinn.io/} \\

    \end{tabbing}

    \vfill
    \leftskip=-\hoffset
    \advance\textwidth\hoffset
    \hsize=\textwidth
    \fullline
    \vskip 2pt

    Source code for document available at
    \url{https://github.com/quinn/resume/blob/master/resume.tex}

\end{resume}
\end{document}
